---
output: html_document
runtime: shiny
---
```{r, echo=FALSE, include=FALSE}
# library(devtools)
# devtools::install_github("JVAdams/jvamisc")
# library(jvamisc)

# library(shinyapps)
# deployApp()

#library(shiny)
#library(LW1949)
```

### Evaluation of Dose-Effect Experiments using LW1949

The R package **[LW1949](https://github.com/JVAdams/LW1949)** automates the manual approach to evaluating dose-effect experiments taken by Litchfield and Wilcoxon (1949).  Automation saves time and yields the best Litchfield Wilcoxon model fit possible, by minimizing the chi-squared statistic.

You can try it out here, by providing information on three key input variables (on the left): the chemical concentration or dose, the number tested, and the number affected. Effective doses will be estimated for the specified percentages affected (on the right).

```{r, echo=FALSE}
output$onePlot <- renderPlot({
  
  dose <- c(input$dose1, input$dose2, input$dose3, input$dose4, input$dose5, 
    input$dose6, input$dose7, input$dose8, input$dose9, input$dose10)
  ntot <- c(input$ntot1, input$ntot2, input$ntot3, input$ntot4, input$ntot5, 
    input$ntot6, input$ntot7, input$ntot8, input$ntot9, input$ntot10)
  nfx <- c(input$nfx1, input$nfx2, input$nfx3, input$nfx4, input$nfx5, 
    input$nfx6, input$nfx7, input$nfx8, input$nfx9, input$nfx10)
  sel <- !is.na(dose) & !is.na(ntot) & !is.na(nfx)
  if (sum(sel) < 1) warning("No rows with non-missing data.")
  if (any(ntot[sel] < 0)) error("No. tested should be greater than zero.")
  if (any(ntot[sel] < nfx[sel])) 
    error("No. affected should not be greater than No. tested.")
  mydat <- dataprep(dose[sel], ntot[sel], nfx[sel])
  
  fLW <- fitLW(mydat)
  pctaffected <- c(input$pa1, input$pa2, input$pa3)
  predLW <- predlinear(pctaffected, fLW)
  
  par(mar=c(4, 4, 1, 0.1))
  plotDE(mydat)
  abline(fLW$params)
  y <- probit(predLW[, "pct"]/100)
  points(log10(predLW[, "ED"]), y, cex=0.7, pch=16, col="red")
  arrows(log10(predLW[, "lower"]), y, log10(predLW[, "upper"]), y, 
    length=0.1, angle=90, code=3, col="red")

}, 
  width=700, 
  height=700,
)
```

```{r, echo=FALSE}
datos <- reactive({
  dose <- c(input$dose1, input$dose2, input$dose3, input$dose4, input$dose5, 
    input$dose6, input$dose7, input$dose8, input$dose9, input$dose10)
  ntot <- c(input$ntot1, input$ntot2, input$ntot3, input$ntot4, input$ntot5, 
    input$ntot6, input$ntot7, input$ntot8, input$ntot9, input$ntot10)
  nfx <- c(input$nfx1, input$nfx2, input$nfx3, input$nfx4, input$nfx5, 
    input$nfx6, input$nfx7, input$nfx8, input$nfx9, input$nfx10)
  sel <- !is.na(dose) & !is.na(ntot) & !is.na(nfx)
  mydat <- dataprep(dose[sel], ntot[sel], nfx[sel])
  
  fLW <- fitLW(mydat)
  pctaffected <- c(input$pa1, input$pa2, input$pa3)
  predlinear(pctaffected, fLW)
  })  

output$oneTable <- renderTable({
  datos()
},
  digits=c(2, 3, 3, 3, 3)
)
```

```{r, echo=FALSE}
fluidPage(
  
  fluidRow(
    column(2, 
      numericInput("dose1", "Dose", value=0.0625),
      numericInput("dose2", NULL, value=0.125),
      numericInput("dose3", NULL, value=0.25),
      numericInput("dose4", NULL, value=0.5),
      numericInput("dose5", NULL, value=1.0),
      numericInput("dose6", NULL, value=NA),
      numericInput("dose7", NULL, value=NA),
      numericInput("dose8", NULL, value=NA),
      numericInput("dose9", NULL, value=NA),
      numericInput("dose10", NULL, value=NA)
    ),
    column(2, 
      numericInput("ntot1", "No. tested", value=8),
      numericInput("ntot2", NULL, value=8),
      numericInput("ntot3", NULL, value=8),
      numericInput("ntot4", NULL, value=8),
      numericInput("ntot5", NULL, value=8),
      numericInput("ntot6", NULL, value=NA),
      numericInput("ntot7", NULL, value=NA),
      numericInput("ntot8", NULL, value=NA),
      numericInput("ntot9", NULL, value=NA),
      numericInput("ntot10", NULL, value=NA)
    ),
    column(2,
      numericInput("nfx1", "No. affected", value=1),
      numericInput("nfx2", NULL, value=4),
      numericInput("nfx3", NULL, value=4),
      numericInput("nfx4", NULL, value=7),
      numericInput("nfx5", NULL, value=8),
      numericInput("nfx6", NULL, value=NA),
      numericInput("nfx7", NULL, value=NA),
      numericInput("nfx8", NULL, value=NA),
      numericInput("nfx9", NULL, value=NA),
      numericInput("nfx10", NULL, value=NA)
    ),
    column(2),
    column(2,
      numericInput("pa1", label="% Affected", value=25),
      numericInput("pa2", label=NULL, value=50),
      numericInput("pa3", label=NULL, value=99.9)
    )
  ),
  fluidRow(
    plotOutput("onePlot", inline=TRUE),
    h5("FIGURE  -  Plot of the observed data with the Litchfield Wilcoxon fitted model on the log10-probit scale. Predicted effective doses with 95% confidence intervals for the specified percentages affected are in red.  Observations with 0% or or 100% affected are plotted at 0.1 and 99.9% respectively using white filled circles.
")
  ),
  fluidRow(
    h5("TABLE  -  Predicted effective doses (with 95% confidence intervals) for the specified percentages affected using the Litchfield Wilcoxon approach."),
    tableOutput("oneTable")
  )
)
```

[Litchfield, J. T. Jr. and F. Wilcoxon. 1949.](http://jpet.aspetjournals.org/content/96/2/99.abstract) A simplified method of evaluating dose-effect experiments. Journal of Pharmacology and Experimental Therapeutics 99(2):99-113.

---

Last modified: 27 May 2015  
Author: Jean V. Adams, [USGS - Great Lakes Science Center](http://www.glsc.usgs.gov/) and [Great Lakes Fishery Commission](http://www.GLFC.org/)

Created with: [R Shiny](http://shiny.rstudio.com/) by [Rstudio](http://www.rstudio.com/)  
